### 2015-04-19 paper/main.tex
Repo: Initial commit, with introduction and related work.

\documentclass[12pt]{memoir}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{simplestyle}
\usepackage{enumitem}

\addbibresource{refs}

\title{Extracting Menu Navigation and Program Configuration Events 
from User Interface Video Tutorials}
\author{Daniel Seita \& Andrew Head}

\begin{document}

\maketitle

\section{Introduction}

\textbf{This work seeks to use video processing and object recognition techniqes as
a technique to mine the usability of an application.}  Given the proliferation
of video tutorials on using different software, this provides new opportunties
to assess what complex actions are frequently performed by a variety of users.
We describe a technique for recognizing menus, detecting that an item has
been clicked in a menu, comparing this menu item to all other instances of
that same item by template matching, and then composing temporally close
menu navigations into configuration tasks.  By working with a corpus of
around 100 tutorials related to setting up the Eclipse environment for
programming tasks, we describe the configuration tasks that are performed
the most often.  We discuss how we can improve this workflow to improve the
speed and accuracy of detection in the future.

\subsection{Motivation}

\textbf{Andrew: Make this have less of a strong focus on the value of
video tutorials, and instead talk about mining usability from online data
sources, such as with CUTS}

Video tutorials have become prevalent for learning software (Matejka et al. 2011, 
Pongnumkul et al. 2010, 1).  Banovic et al. claim this may be because users 
can directly observe expert use, which can serve as a strong learning aid 
(Shneiderman 1983, (1, 4)).  Grossman \& Fitzmaurice showed benefits of short 
contextual video clips (Grossman \& Fitzmaurice 2010, 1).  Short, 10-25 second 
contextually available videos were effective to help users accomplish task and 
retain what they learned than traditional text-based tutorials (Grossman \& 
Fitzmaurice 2010, 4).

Though they also have their drawbacks (Hategekimana et al. 2008, 4):  
Navigation issues could lead to misunderstanding of content (Harrison 1995, 
(1, 4)), and users may not be able to keep up with the pace of the content 
(Palmiter \& Elkerton 1991, 1).  Researchers working with longer, 2-3 minute 
task-oriented tutorials found that users performed better with text tutorials 
than videos because users could not work at the same pace as the video 
(Grabler et al. 2009, 4).  Almost all research on instructional videos point 
to a need for segmented videos that emphasize each step of the task (4).

\section{Related Work}

\textbf{Andrew: This should all use citations, not parentheses.}

\subsection{Reverse Engineering UIs}

Runtime modification of existing interfaces is one application of reverse 
engineeing UIs.  For example, replacing the toolkit drawing object and 
intercepting commands (Edwards et al. 1997, Olsen et al. 1999, 2).  Others 
have used interface introspection using the accessibility API 
(Stuerzlinger et al. 2006, 2).  Others have dynamically loaded code into 
the program space, for example with Scotty (Eagan et al. 2011, 2).

Sikuli (Yeh et al. 2009, 1) uses computer vision to identify GUI elements from 
screen captures, using template matching and voting based on invariant local 
features (Yeh et al. 2009, 2).  Sikuli also searches for UI elements in the 
interface (Bergman et al. 2005, 1), and automates GUI tasks (Chang et al. 2010, 
1).  For searching based on screenshots, 3 types of features are extracted: 
text from the source document, visual words computed from visual words from 
MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
text extracted through OCR (4).  For searching on the screen for saved 
screenshot images, small patterns are found via template matching and large 
patterns through invariant feature voting (4).

Pause-and-Play extends the template matching approach of Sikuli to detect 
tool-selection UI events in compressed, low-resolution video tutorials.  
The system takes a tool palette template and tool icons as input, 
producing metadata file of tool changes with timecodes.  With template 
matching at multiple resolutions, detection is invariant to recording 
resolution and some camera effects.  Their system cannot be run in in 
real-time (3).

A number of different technologies attempt to learn templates for UI 
elements (Chang et al. 2011, Dixon \& Fogarty 2010, Hurst et al. 2010, 
Matejka et al. 2011, 1), using information from mouse APIs (Hurst et al. 
2010, 1) and accessibility APIs (Chang et al. 2011).  Prefab identifies GUI 
elements with GUI specific visual features (Dixon \& Fogarty 2010, 1), which 
enables overlay of advanced interactions on existing interfaces (Dixon et al. 
2011, Dixon et al. 2012, 1).  Waken contributes to this space by discovering 
cursor shapes, clicking actions, icons, tooltips and menus, all by examining 
the difference between frames of UI video.  They do this by making assumptions 
about how the image of icons change during hover and press actions.  Detection 
of the cursor and icons in later frames is performed by template matching (1).

Pixel-based methods for reverse engineering UIs are motivated by their 
indepenedece from underlying application or toolkit requirements (2).  Work 
by Zettleymoyer et al. (Zettlemoyer et al. 1998, Zettlmoyer et al. 1999, 2) 
examine widget identification in IBOTS and VisMap and in programming by 
example (St. Amant et al., Potter, St. Amant et al. 2005, 2).  Olsen et al.'s 
ScreenCrayons links ink annotations to arbitrary screen elements (Olsen et al. 
2004, 2), and Tan et al.'s work interactively subdivides windows with a 
copy-paste metaphor (Tan et al. 2004, 2).

To delve into the technical implementations of the Prefab pixel-based 
matching algorithm, we report from (2).  Prefab identifies interface elements 
with a library of prototypes.  This uses two strategies: exact matches of 
prototype pixels against an image, and modelining the prototype background 
and differencing pixel in an image to identify foreground interface elements.  
Prefab generalizes from example images to models which contain parts like 
exact pixel features, or regions or areas of variable size or repeating 
patterns.  It organizes the entire interface into a hierarchy (2).

\subsection{Action Recognition}

Work here by Jitendra and Georgia and beyond.

\section{Data}

Answer these questions:
\begin{enumerate}[noitemsep]
\item What is our dataset?
\item How did we construct/acquire it?
\item What's its size?
\item (optional) How will we improve it in the future?
\end{enumerate}

\section{Implementation}
Here's a figure of our pipeline.  \textbf{Andrew: Add figure of pipeline.}

\section{Results}

Here we want to touch upon:
\begin{enumerate}[noitemsep]
\item How reliably can we classify UI events?
\item How long does it take for us to process one minute of video?  What are
the practical implications of this?
\item Some images that show recognition results for a few representative
screenshots of user interfaces.
\end{enumerate}

\section{Discussion}

\subsection{Limitations}

\subsection{Future Directions}

\section{Conclusion}

We freakin' rock.

\section{References}
\printbibliography[heading=none]

\end{document}

### 2015-04-20 paper/main.tex
Paper: added citations in BibTeX

@@
 
+Recent research has focused on how to improve the use of video tutorials 
+to help users learn software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  
+One strength of video tutorials may be that users
+can directly observe expert use, which can serve as a strong learning aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short 
+contextual video clips.  Short, 10-25 second 
+contextually available videos were effective to help users accomplish task and 
+retain what they learned than traditional text-based tutorials~\cite{grossman_toolclips_2010}.
+
+However, video tutorials have drawbacks:
+Navigation issues could lead to misunderstanding of content~\cite{harrison_comparison_1995}.
+Users may not be able to keep up with the pace of the content~\cite{palmiter_evaluation_1991}.
+Researchers working with longer, 2-3 minute 
+task-oriented tutorials found that users performed better with text tutorials 
+than videos because users could not work at the same pace as the video~\cite{grabler_generating_2009}.
+In general, research on instructional videos point shows a need to segmented videos to
+emphasize the steps of the task.
+
 \textbf{Andrew: Make this have less of a strong focus on the value of
@@
 
-Video tutorials have become prevalent for learning software (Matejka et al. 2011, 
-Pongnumkul et al. 2010, 1).  Banovic et al. claim this may be because users 
-can directly observe expert use, which can serve as a strong learning aid 
-(Shneiderman 1983, (1, 4)).  Grossman \& Fitzmaurice showed benefits of short 
-contextual video clips (Grossman \& Fitzmaurice 2010, 1).  Short, 10-25 second 
-contextually available videos were effective to help users accomplish task and 
-retain what they learned than traditional text-based tutorials (Grossman \& 
-Fitzmaurice 2010, 4).
-
-Though they also have their drawbacks (Hategekimana et al. 2008, 4):  
-Navigation issues could lead to misunderstanding of content (Harrison 1995, 
-(1, 4)), and users may not be able to keep up with the pace of the content 
-(Palmiter \& Elkerton 1991, 1).  Researchers working with longer, 2-3 minute 
-task-oriented tutorials found that users performed better with text tutorials 
-than videos because users could not work at the same pace as the video 
-(Grabler et al. 2009, 4).  Almost all research on instructional videos point 
-to a need for segmented videos that emphasize each step of the task (4).
-
 \section{Related Work}
 
-\textbf{Andrew: This should all use citations, not parentheses.}
+\subsection{Visually Reverse Engineering UIs}
 
-\subsection{Reverse Engineering UIs}
+By examining pixels, many have succeeded at reverse engineering user interfaces
+and interactions with user interfaces with purely visual information, independent
+of any knowledge of underlying application implementation. Work 
+by Zettleymoyer et al.~\cite{zettlemoyer_ibots_1999}~\cite{zettlemoyer_visual_1999}
+examine widget identification in IBOTS and VisMap.  Also see~\cite{potter_triggers_1992}~\cite{amant_image_2005}~\cite{lieberman_visual_2001}. 
+Visual identification of widgets and UIs may also have also been used in Olsen 
+et al.'s ScreenCrayons work that links annotations to arbitrary screen 
+elements~\cite{olsen_jr_implementing_1999},
+and in Tan et al.'s work to interactively subdivide windows with a 
+copy-paste metaphor~\cite{tan_wincuts_2004}.
+\textbf{Andrew: Check on this.}
 
-Runtime modification of existing interfaces is one application of reverse 
-engineeing UIs.  For example, replacing the toolkit drawing object and 
-intercepting commands (Edwards et al. 1997, Olsen et al. 1999, 2).  Others 
-have used interface introspection using the accessibility API 
-(Stuerzlinger et al. 2006, 2).  Others have dynamically loaded code into 
-the program space, for example with Scotty (Eagan et al. 2011, 2).
-
-Sikuli (Yeh et al. 2009, 1) uses computer vision to identify GUI elements from 
-screen captures, using template matching and voting based on invariant local 
-features (Yeh et al. 2009, 2).  Sikuli also searches for UI elements in the 
-interface (Bergman et al. 2005, 1), and automates GUI tasks (Chang et al. 2010, 
-1).  For searching based on screenshots, 3 types of features are extracted: 
-text from the source document, visual words computed from visual words from 
-MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
-text extracted through OCR (4).  For searching on the screen for saved 
+More recently, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to 
+identify GUI elements from screen captures, using template matching for small
+UI elements and voting based on invariant local features for large elements.
+In application, Sikuli allows users to search for documentation related to
+screenshots taken of UI elements, and to script GUI tasks using visual
+cues of the UI.  For searching based on screenshots, 3 types of features are 
+extracted: text from the source document, visual words computed from visual 
+words from MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
+text extracted through OCR.  For searching on the screen for saved 
 screenshot images, small patterns are found via template matching and large 
-patterns through invariant feature voting (4).
+patterns through invariant feature voting.
 
@@
 resolution and some camera effects.  Their system cannot be run in in 
-real-time (3).
+real-time~\cite{pongnumkul_pause-and-play_2011}.
 
-A number of different technologies attempt to learn templates for UI 
-elements (Chang et al. 2011, Dixon \& Fogarty 2010, Hurst et al. 2010, 
-Matejka et al. 2011, 1), using information from mouse APIs (Hurst et al. 
-2010, 1) and accessibility APIs (Chang et al. 2011).  Prefab identifies GUI 
-elements with GUI specific visual features (Dixon \& Fogarty 2010, 1), which 
-enables overlay of advanced interactions on existing interfaces (Dixon et al. 
-2011, Dixon et al. 2012, 1).  Waken contributes to this space by discovering 
+A number of different technologies attempt to learn templates for arbitrary UI 
+elements~\cite{chang_associating_2011}~\cite{dixon_prefab_2010}~\cite{hurst_automatically_2010}~\cite{matejka_ambient_2011}.
+Learning may require access to mouse APIs~\cite{hurst_automatically_2010}
+and accessibility APIs~\cite{chang_associating_2011}.
+
+Prefab identifies GUI elements with GUI specific visual features~\cite{dixon_prefab_2010}, which 
+enables overlay of advanced interactions on existing interfaces~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
+\textbf{Andrew: Check up on this initial description.  I'm also not sure
+if Prefab actually belongs in this conceptual group.}
+To delve into the technical implementations of the Prefab pixel-based 
+matching algorithm, we report from~\cite{dixon_general-purpose_2012}.
+Prefab identifies interface elements using a library of prototypes.  
+This uses two strategies: exact matches of prototype pixels against an image,
+and modelining the prototype background and differencing pixel in an image 
+to identify foreground interface elements.  
+Prefab generalizes from example images to models which contain parts like 
+exact pixel features, or regions or areas of variable size or repeating 
+patterns.  It organizes the entire interface into a hierarchy.
+
+Waken contributes to this space by discovering 
 cursor shapes, clicking actions, icons, tooltips and menus, all by examining 
@@
 about how the image of icons change during hover and press actions.  Detection 
-of the cursor and icons in later frames is performed by template matching (1).
-
-Pixel-based methods for reverse engineering UIs are motivated by their 
-indepenedece from underlying application or toolkit requirements (2).  Work 
-by Zettleymoyer et al. (Zettlemoyer et al. 1998, Zettlmoyer et al. 1999, 2) 
-examine widget identification in IBOTS and VisMap and in programming by 
-example (St. Amant et al., Potter, St. Amant et al. 2005, 2).  Olsen et al.'s 
-ScreenCrayons links ink annotations to arbitrary screen elements (Olsen et al. 
-2004, 2), and Tan et al.'s work interactively subdivides windows with a 
-copy-paste metaphor (Tan et al. 2004, 2).
-
-To delve into the technical implementations of the Prefab pixel-based 
-matching algorithm, we report from (2).  Prefab identifies interface elements 
-with a library of prototypes.  This uses two strategies: exact matches of 
-prototype pixels against an image, and modelining the prototype background 
-and differencing pixel in an image to identify foreground interface elements.  
-Prefab generalizes from example images to models which contain parts like 
-exact pixel features, or regions or areas of variable size or repeating 
-patterns.  It organizes the entire interface into a hierarchy (2).
+of the cursor and icons in later frames is performed by template matching~\cite{banovic_waken_2012}.
+We rely on techniques similar to those in Waken to establish when menus
+have been activated and menu items selected.
 

### 2015-04-27 eval/e3/fetchvideos.sh
Evaluations: #3, labeled events from 3.5 tutorials.  Moving on to E4.

@@ -32,7 +32,7 @@ do
   echo "=== Downloading video $vid ==="
   youtube-dl \
     --rate-limit $RATE_LIMIT \
-    -f "best[height=$HEIGHT]" \
+    -f "best[height=$HEIGHT]+bestaudio" \
     -o "videos/V%(id)s-%(title)s-%(format)s.%(ext)s" \
     --restrict-filenames \
     --no-overwrites \

### 2015-04-27 eval/e4/fetchvideos.sh
Evaluations: #4, started, watched videos 1-11 of tutorial sequence.

@@ -1,0 +1,18 @@
+#! /bin/bash
+
+RATE_LIMIT='400k'
+HEIGHT='480'
+YOUTUBE="https://www.youtube.com/"
+TARGET="playlist?list=PLF03C6B2C0B292A1E"
+OUTDIR="videos"
+LOGFILE=".download.log"
+
+youtube-dl \
+  --rate-limit $RATE_LIMIT \
+  -f "best[height=$HEIGHT]+bestaudio" \
+  -o "videos/%(autonumber)s-%(id)s-%(title)s.%(ext)s" \
+  --restrict-filenames \
+  --no-overwrites \
+  --ignore-errors \
+  $YOUTUBE$TARGET \
+  2>&1 | tee -a $LOGFILE

### 2015-04-27 eval/e5/fetchvideos.sh
Evaluations: #5, got frames of menu appearance and bounding rects.

@@ -1,0 +1,28 @@
+#! /bin/bash
+
+RATE_LIMIT='400k'
+HEIGHT='480'
+YOUTUBE="https://www.youtube.com/watch?v="
+OUTDIR="videos"
+VID_IDS=(
+'vXcC533_IcQ'
+'o1vRJ07KDZ0'
+'-MBS2YvUY2M'
+'p9KRJoX13vo'
+'ok8mZW_BDG4'
+)
+LOGFILE='.download.log'
+
+for vid in "${VID_IDS[@]}"
+do
+  echo "=== Downloading video $vid ==="
+  youtube-dl \
+    --rate-limit $RATE_LIMIT \
+    -f "best[height=$HEIGHT]+bestaudio" \
+    -o "videos/%(autonumber)s-%(id)s-%(title)s.%(ext)s" \
+    --autonumber-size 1 \
+    --restrict-filenames \
+    --no-overwrites \
+    "$YOUTUBE$vid" \
+    2>&1 | tee -a $LOGFILE
+done

### 2015-05-10 paper/main.tex
Evaluations: #5, added code to run detection on 5 videos.
Modified some results and cleaned up/organized the writeup

@@
-\documentclass[12pt]{memoir}
+\documentclass[10pt]{article}
 \usepackage[backend=bibtex,style=numeric]{biblatex}
-\usepackage{simplestyle}
+%\usepackage{simplestyle}
 \usepackage{enumitem}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{fullpage}
 
@@
 
-\title{Extracting Menu Navigation and Program Configuration Events 
-from User Interface Video Tutorials}
+\title{Extracting Application and Menu Events from UI Tutorial Videos}
 \author{Daniel Seita \& Andrew Head}
@@
 
-\textbf{This work seeks to use video processing and object recognition techniqes as
-a technique to mine the usability of an application.}  Given the proliferation
-of video tutorials on using different software, this provides new opportunties
-to assess what complex actions are frequently performed by a variety of users.
-We describe a technique for recognizing menus, detecting that an item has
-been clicked in a menu, comparing this menu item to all other instances of
-that same item by template matching, and then composing temporally close
-menu navigations into configuration tasks.  By working with a corpus of
-around 100 tutorials related to setting up the Eclipse environment for
-programming tasks, we describe the configuration tasks that are performed
-the most often.  We discuss how we can improve this workflow to improve the
-speed and accuracy of detection in the future.
+This work seeks to use video processing and object recognition techniques as a technique to
+mine the usability of an application.  Given the proliferation of video tutorials on using
+different software, this provides new opportunities to assess what complex actions are frequently
+performed by a variety of users.  We describe a technique for recognizing menus, detecting that an
+item has been clicked in a menu, comparing this menu item to all other instances of that same item
+by template matching, and then composing temporally close menu navigations into configuration tasks.
+By working with a corpus of around 100 tutorials related to setting up the Eclipse environment for
+programming tasks, we describe the configuration tasks that are performed the most often.  We
+discuss how we can improve this workflow to improve the speed and accuracy of detection in the
+future.
 
-\subsection{Motivation}
+Our contributions include a small but effective dataset for evaluating the effectiveness of
+detectors of UI menu-opening actions.
 
-Recent research has focused on how to improve the use of video tutorials 
-to help users learn software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  
-One strength of video tutorials may be that users
-can directly observe expert use, which can serve as a strong learning aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short 
-contextual video clips.  Short, 10-25 second 
-contextually available videos were effective to help users accomplish task and 
-retain what they learned than traditional text-based tutorials~\cite{grossman_toolclips_2010}.
+Recent research has focused on how to improve the use of video tutorials to help users learn
+software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  One strength of video
+tutorials may be that users can directly observe expert use, which can serve as a strong learning
+aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short contextual
+video clips.  Short, 10-25 second contextually available videos were effective to help users
+accomplish task and retain what they learned than traditional text-based
+tutorials~\cite{grossman_toolclips_2010}.
 
-However, video tutorials have drawbacks:
-Navigation issues could lead to misunderstanding of content~\cite{harrison_comparison_1995}.
-Users may not be able to keep up with the pace of the content~\cite{palmiter_evaluation_1991}.
-Researchers working with longer, 2-3 minute 
-task-oriented tutorials found that users performed better with text tutorials 
-than videos because users could not work at the same pace as the video~\cite{grabler_generating_2009}.
-In general, research on instructional videos point shows a need to segmented videos to
-emphasize the steps of the task.
+However, video tutorials have drawbacks: Navigation issues could lead to misunderstanding of
+content~\cite{harrison_comparison_1995}.  Users may not be able to keep up with the pace of the
+content~\cite{palmiter_evaluation_1991}.  Researchers working with longer, 2-3 minute task-oriented
+tutorials found that users performed better with text tutorials than videos because users could not
+work at the same pace as the video~\cite{grabler_generating_2009}.  In general, research on
+instructional videos point shows a need to segmented videos to emphasize the steps of the task.
 
-\textbf{Andrew: Make this have less of a strong focus on the value of
-video tutorials, and instead talk about mining usability from online data
-sources, such as with CUTS}
+\textbf{Andrew: Make this have less of a strong focus on the value of video tutorials, and instead
+talk about mining usability from online data sources, such as with CUTS}
 
 \section{Related Work}
-
-\subsection{Visually Reverse Engineering UIs}
 
@@
 
-\subsection{Action Recognition}
+\section{Video Classification}
 
-Work here by Jitendra and Georgia and beyond.
+This will be Daniel's section. I'm probably not going to include any subsections to save time.
 
-\section{Data}
+Figure~\ref{fig:alex_net} shows our accuracy results for the two AlexNet networks we trained.
+
+Figure~\ref{fig:per_class} shows our per-class accuracy results for the ``no noise'' AlexNet
+network.
+
+\begin{figure}
+\centering
+  \begin{minipage}{.45\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{AlexNet_Accuracy}
+  \caption{AlexNet accuracy results of two networks trained on two image datasets.}
+  \label{fig:alex_net}
+  \end{minipage}\hfill
+  \begin{minipage}{.45\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{PerClassPerformance}
+  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
+  \label{fig:per_class}
+  \end{minipage}
+\end{figure}
+
+Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
+the first layer of AlexNet, each of which has dimension $55\times 55$.
+
+\begin{figure}
+\centering
+  \begin{minipage}{.4\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Filters_All}
+  \caption{Visualization of filters from the network trained on all our image data.}
+  \label{fig:filters_all}
+  \end{minipage}\hfill
+  \begin{minipage}{.4\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Filters_NoNoise}
+  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
+  \label{fig:filters_nonoise}
+  \end{minipage}
+\end{figure}
+
+\section{Locating Menus in a Frame Sequence}
+
+This will be Andrew's section.
+
+\subsection{Data}
 
@@
 
-\section{Implementation}
-Here's a figure of our pipeline.  \textbf{Andrew: Add figure of pipeline.}
+\subsection{Implementation}
+Here's a figure of our (edit: Andrew's) pipeline.  \textbf{Andrew: Add figure of pipeline.}
 
-\section{Results}
+\subsection{Menu Location Results}
 
-Here we want to touch upon:
+Here we (edit: Andrew) want to touch upon:
 \begin{enumerate}[noitemsep]
@@
 
-\section{Discussion}
+\section{Discussion and Conclusion}
 
-\subsection{Limitations}
-
-\subsection{Future Directions}
-
-\section{Conclusion}
+TODO (combining the two because we don't have a lot of space!)
 
@@
 
-\section{References}
-\printbibliography[heading=none]
+\printbibliography
 

### 2015-05-10 paper/main.tex
Modified filters for 1000 iterations

@@
 \usepackage[backend=bibtex,style=numeric]{biblatex}
-%\usepackage{simplestyle}
 \usepackage{enumitem}
@@
 
-This work seeks to use video processing and object recognition techniques as a technique to
-mine the usability of an application.  Given the proliferation of video tutorials on using
-different software, this provides new opportunities to assess what complex actions are frequently
-performed by a variety of users.  We describe a technique for recognizing menus, detecting that an
-item has been clicked in a menu, comparing this menu item to all other instances of that same item
-by template matching, and then composing temporally close menu navigations into configuration tasks.
-By working with a corpus of around 100 tutorials related to setting up the Eclipse environment for
-programming tasks, we describe the configuration tasks that are performed the most often.  We
-discuss how we can improve this workflow to improve the speed and accuracy of detection in the
-future.
+In this project, we present two main contributions. First, we show that a standard neural network
+following the AlexNet architecture with minimal tweaking can accurately recognize frames belonging
+to a class of videos.  Second, we present a pipeline and procedure for detecting menus within a
+video frame sequence. We then discuss how these two stages might be combined to enhance the process
+of extracting useful information from videos.
 
-Our contributions include a small but effective dataset for evaluating the effectiveness of
-detectors of UI menu-opening actions.
+\subsection{Motivation}
 
-Recent research has focused on how to improve the use of video tutorials to help users learn
-software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  One strength of video
-tutorials may be that users can directly observe expert use, which can serve as a strong learning
-aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short contextual
-video clips.  Short, 10-25 second contextually available videos were effective to help users
-accomplish task and retain what they learned than traditional text-based
-tutorials~\cite{grossman_toolclips_2010}.
+The proliferation of video tutorials on using different software raises new research questions on
+how to improve their use to help users learn software~\cite{matejka_ambient_2011,
+pongnumkul_pause-and-play_2011}.  One strength of video tutorials may be that users can directly
+observe expert use, which can serve as a strong learning aid. Grossman \& Fitzmaurice showed
+benefits of brief contextual video clips: short, 10-25 second contextually available videos were
+effective to help users accomplish task and retain what they learned than traditional text-based
+tutorials~\cite{grossman_toolclips_2010}. Unfortunately, video tutorials have drawbacks. Navigation
+issues could lead to misunderstanding of content, and users may not be able to keep up with the pace
+of instruction. Researchers working with longer, 2-3 minute task-oriented tutorials found that users
+performed better with text tutorials than videos because users could not work at the same pace as
+the video~\cite{grabler_generating_2009}.
 
-However, video tutorials have drawbacks: Navigation issues could lead to misunderstanding of
-content~\cite{harrison_comparison_1995}.  Users may not be able to keep up with the pace of the
-content~\cite{palmiter_evaluation_1991}.  Researchers working with longer, 2-3 minute task-oriented
-tutorials found that users performed better with text tutorials than videos because users could not
-work at the same pace as the video~\cite{grabler_generating_2009}.  In general, research on
-instructional videos point shows a need to segmented videos to emphasize the steps of the task.
+In general, research on instructional videos point shows a need to segmented videos to emphasize the
+steps of the task. One way to do that might be to develop techniques for detecting locations of
+certain menu actions in the video, such as when the video shows its user clicking on a button in a
+Photoshop video to create a blank image. Our goal, therefore, is to utilize computer vision
+techniques to aid in this process.
 
-\textbf{Andrew: Make this have less of a strong focus on the value of video tutorials, and instead
-talk about mining usability from online data sources, such as with CUTS}
+\subsection{Related Work}
 
-\section{Related Work}
-
-By examining pixels, many have succeeded at reverse engineering user interfaces
-and interactions with user interfaces with purely visual information, independent
-of any knowledge of underlying application implementation. Work 
-by Zettleymoyer et al.~\cite{zettlemoyer_ibots_1999}~\cite{zettlemoyer_visual_1999}
-examine widget identification in IBOTS and VisMap.  Also see~\cite{potter_triggers_1992}~\cite{amant_image_2005}~\cite{lieberman_visual_2001}. 
-Visual identification of widgets and UIs may also have also been used in Olsen 
-et al.'s ScreenCrayons work that links annotations to arbitrary screen 
-elements~\cite{olsen_jr_implementing_1999},
-and in Tan et al.'s work to interactively subdivide windows with a 
-copy-paste metaphor~\cite{tan_wincuts_2004}.
+By examining pixels, many have succeeded at reverse engineering user interfaces and interactions
+with user interfaces with purely visual information, independent of any knowledge of underlying
+application implementation. Work by Zettleymoyer et
+al.~\cite{zettlemoyer_ibots_1999}~\cite{zettlemoyer_visual_1999} examine widget identification in
+IBOTS and VisMap.  Also
+see~\cite{potter_triggers_1992}~\cite{amant_image_2005}~\cite{lieberman_visual_2001}.  Visual
+identification of widgets and UIs may also have also been used in Olsen et al.'s ScreenCrayons work
+that links annotations to arbitrary screen elements~\cite{olsen_jr_implementing_1999}, and in Tan et
+al.'s work to interactively subdivide windows with a copy-paste metaphor~\cite{tan_wincuts_2004}.
 \textbf{Andrew: Check on this.}
 
-More recently, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to 
-identify GUI elements from screen captures, using template matching for small
-UI elements and voting based on invariant local features for large elements.
-In application, Sikuli allows users to search for documentation related to
-screenshots taken of UI elements, and to script GUI tasks using visual
-cues of the UI.  For searching based on screenshots, 3 types of features are 
-extracted: text from the source document, visual words computed from visual 
-words from MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
-text extracted through OCR.  For searching on the screen for saved 
-screenshot images, small patterns are found via template matching and large 
-patterns through invariant feature voting.
+More recently, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI elements from
+screen captures, using template matching for small UI elements and voting based on invariant local
+features for large elements.  In application, Sikuli allows users to search for documentation
+related to screenshots taken of UI elements, and to script GUI tasks using visual cues of the UI.
+For searching based on screenshots, 3 types of features are extracted: text from the source
+document, visual words computed from visual words from MSER-detected salient elliptical patches, and
+3-grams over widget-embedded text extracted through OCR.  For searching on the screen for saved
+screenshot images, small patterns are found via template matching and large patterns through
+invariant feature voting.
 
-Pause-and-Play extends the template matching approach of Sikuli to detect 
-tool-selection UI events in compressed, low-resolution video tutorials.  
-The system takes a tool palette template and tool icons as input, 
-producing metadata file of tool changes with timecodes.  With template 
-matching at multiple resolutions, detection is invariant to recording 
-resolution and some camera effects.  Their system cannot be run in in 
-real-time~\cite{pongnumkul_pause-and-play_2011}.
+Pause-and-Play extends the template matching approach of Sikuli to detect tool-selection UI events
+in compressed, low-resolution video tutorials.  The system takes a tool palette template and tool
+icons as input, producing metadata file of tool changes with timecodes.  With template matching at
+multiple resolutions, detection is invariant to recording resolution and some camera effects.  Their
+system cannot be run in in real-time~\cite{pongnumkul_pause-and-play_2011}.
 
@@
 elements~\cite{chang_associating_2011}~\cite{dixon_prefab_2010}~\cite{hurst_automatically_2010}~\cite{matejka_ambient_2011}.
-Learning may require access to mouse APIs~\cite{hurst_automatically_2010}
-and accessibility APIs~\cite{chang_associating_2011}.
+Learning may require access to mouse APIs~\cite{hurst_automatically_2010} and accessibility
+APIs~\cite{chang_associating_2011}.
 
 Prefab identifies GUI elements with GUI specific visual features~\cite{dixon_prefab_2010}, which
-enables overlay of advanced interactions on existing interfaces~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
-\textbf{Andrew: Check up on this initial description.  I'm also not sure
-if Prefab actually belongs in this conceptual group.}
-To delve into the technical implementations of the Prefab pixel-based 
-matching algorithm, we report from~\cite{dixon_general-purpose_2012}.
-Prefab identifies interface elements using a library of prototypes.  
-This uses two strategies: exact matches of prototype pixels against an image,
-and modelining the prototype background and differencing pixel in an image 
-to identify foreground interface elements.  
-Prefab generalizes from example images to models which contain parts like 
-exact pixel features, or regions or areas of variable size or repeating 
-patterns.  It organizes the entire interface into a hierarchy.
+enables overlay of advanced interactions on existing
+interfaces~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.  \textbf{Andrew: Check up on
+this initial description.  I'm also not sure if Prefab actually belongs in this conceptual group.}
+To delve into the technical implementations of the Prefab pixel-based matching algorithm, we report
+from~\cite{dixon_general-purpose_2012}.  Prefab identifies interface elements using a library of
+prototypes.  This uses two strategies: exact matches of prototype pixels against an image, and
+modelining the prototype background and differencing pixel in an image to identify foreground
+interface elements.  Prefab generalizes from example images to models which contain parts like exact
+pixel features, or regions or areas of variable size or repeating patterns.  It organizes the entire
+interface into a hierarchy.
 
-Waken contributes to this space by discovering 
-cursor shapes, clicking actions, icons, tooltips and menus, all by examining 
-the difference between frames of UI video.  They do this by making assumptions 
-about how the image of icons change during hover and press actions.  Detection 
-of the cursor and icons in later frames is performed by template matching~\cite{banovic_waken_2012}.
-We rely on techniques similar to those in Waken to establish when menus
-have been activated and menu items selected.
+Waken contributes to this space by discovering cursor shapes, clicking actions, icons, tooltips and
+menus, all by examining the difference between frames of UI video.  They do this by making
+assumptions about how the image of icons change during hover and press actions.  Detection of the
+cursor and icons in later frames is performed by template matching~\cite{banovic_waken_2012}.  We
+rely on techniques similar to those in Waken to establish when menus have been activated and menu
+items selected.
 
@@
 Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
-the first layer of AlexNet, each of which has dimension $55\times 55$.
+the first layer of AlexNet, each of which has dimension $55\times 55$. These were taken for the
+model that had 1000 iterations of training.
 
@@
 \centering
-  \begin{minipage}{.4\textwidth}
+  \begin{minipage}{.45\textwidth}
   \centering
-  \includegraphics[width=1\linewidth]{Filters_All}
+  \includegraphics[width=1\linewidth]{Filters_All1000}
   \caption{Visualization of filters from the network trained on all our image data.}
@@
   \end{minipage}\hfill
-  \begin{minipage}{.4\textwidth}
+  \begin{minipage}{.45\textwidth}
   \centering
-  \includegraphics[width=1\linewidth]{Filters_NoNoise}
+  \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
   \caption{Visualization of filters from the network trained on ``no noise'' image data.}

### 2015-05-10 paper/main.tex
Finished with the accuracy on test data. Now will apply to *real* data and that will be it for experiments.
Finished with experiments. Now I will clean up the introductory section and my personal section

@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-  \begin{minipage}{.45\textwidth}
+  \begin{minipage}{.48\textwidth}
   \centering
-  \includegraphics[width=1\linewidth]{AlexNet_Accuracy}
+  \includegraphics[width=1\linewidth]{AlexNet_Accuracy1000}
   \caption{AlexNet accuracy results of two networks trained on two image datasets.}
@@
   \end{minipage}\hfill
-  \begin{minipage}{.45\textwidth}
+  \begin{minipage}{.48\textwidth}
   \centering
-  \includegraphics[width=1\linewidth]{PerClassPerformance}
+  \includegraphics[width=1\linewidth]{PerClassPerformance1000}
   \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
-  \begin{minipage}{.45\textwidth}
+  \begin{minipage}{.4\textwidth}
   \centering
@@
   \end{minipage}\hfill
-  \begin{minipage}{.45\textwidth}
+  \begin{minipage}{.4\textwidth}
   \centering
@@
 \end{figure}
+
+Finally, we performed a brief, informal experiment where we applied the neural network to videos that
+were not part of our training or testing data. We chose one video for each of the four classes by
+searching on Google Video ``X tutorial'' where ``X'' was replaced by one of the four video names.
+The first video that was between 5 and 20 minutes long, and that was not already part of our
+training/testing data, was selected. We extracted one frame per second for the four videos, and
+deleted the first ten and final ten frames from consideration.
+
+To classify the frames, we applied our AlexNet neural network trained on the ``noiseless'' data
+after 1000 iterations. To describe the output, we use ``splits'' where $(a,b,c,d)$ indicates that
+$a, b, c,$ and $d$ frames were classified as Eclipse, Excel, Photoshop, and SketchUp, respectively.
+The splits were as follows: the Eclipse video had $(319,0,79,0)$, the Excel video had
+$(610,0,71,7)$, the Photoshop had $(1,6,416,69)$, and the SketchUp had $(9,2,233,804)$. Clearly, for
+the Eclipse, Photoshop, and SketchUp videos, the classifer was able to assign the vast majority of
+frames to the correct class. If we were using this as part of an overall data mining pipeline, our
+classifier would assign the video according to the most-assigned class, so three videos would be
+classified correctly.
+
+The Excel output is interesting, because our network thought most of the frames belonged to Eclipse
+videos. A brief look at the video indicated that it had an introductory scene that took up ninety
+seconds (and we only deleted the first 10 frames) and that it was about a newer version of Excel
+(2013) than the ones that were trained in our network (2007). Still, it is unfortunate but shows
+that we need to be able to provide a wider variety of training data.
 

### 2015-05-11 paper/main.tex
Cleaned up first two sections, also deleted some info from references to cut down bibliography size

@@
 following the AlexNet architecture with minimal tweaking can accurately recognize frames belonging
-to a class of videos.  Second, we present a pipeline and procedure for detecting menus within a
-video frame sequence. We then discuss how these two stages might be combined to enhance the process
-of extracting useful information from videos.
+to a class of videos.  Second, we present a pipeline for detecting menus within a video frame
+sequence. We then discuss how these two stages might be combined to enhance the process of
+extracting information from videos.
 
@@
 The proliferation of video tutorials on using different software raises new research questions on
-how to improve their use to help users learn software~\cite{matejka_ambient_2011,
-pongnumkul_pause-and-play_2011}.  One strength of video tutorials may be that users can directly
-observe expert use, which can serve as a strong learning aid. Grossman \& Fitzmaurice showed
-benefits of brief contextual video clips: short, 10-25 second contextually available videos were
-effective to help users accomplish task and retain what they learned than traditional text-based
-tutorials~\cite{grossman_toolclips_2010}. Unfortunately, video tutorials have drawbacks. Navigation
-issues could lead to misunderstanding of content, and users may not be able to keep up with the pace
-of instruction. Researchers working with longer, 2-3 minute task-oriented tutorials found that users
-performed better with text tutorials than videos because users could not work at the same pace as
-the video~\cite{grabler_generating_2009}.
+how to improve users' ability to learn from them~\cite{matejka_ambient_2011,
+pongnumkul_pause-and-play_2011}.  One strength of video tutorials is that users can directly observe
+expert use, which can serve as a strong learning aid. Grossman \& Fitzmaurice showed that short,
+10-25 second contextually-related videos were more effective to help users accomplish tasks than
+traditional text-based tutorials~\cite{grossman_toolclips_2010}.  Unfortunately, video tutorials
+have drawbacks. Navigation issues could lead to misunderstanding of content, and users may not be
+able to keep up with the pace of instruction. Researchers working with longer, 2-3 minute
+task-oriented tutorials found that users performed better with text tutorials than videos because
+users could not work at the same pace as the video~\cite{grabler_generating_2009}.
 
-In general, research on instructional videos point shows a need to segmented videos to emphasize the
-steps of the task. One way to do that might be to develop techniques for detecting locations of
-certain menu actions in the video, such as when the video shows its user clicking on a button in a
-Photoshop video to create a blank image. Our goal, therefore, is to utilize computer vision
-techniques to aid in this process.
+In general, research on instructional videos point shows a need to segment videos to emphasize
+certain steps. One way to automatically segment existing videos is to develop techniques for
+detecting locations of certain menu actions in videos. Our goal, therefore, is to do this by
+utilizing computer vision techniques.
 
@@
 By examining pixels, many have succeeded at reverse engineering user interfaces and interactions
-with user interfaces with purely visual information, independent of any knowledge of underlying
-application implementation. Work by Zettleymoyer et
-al.~\cite{zettlemoyer_ibots_1999}~\cite{zettlemoyer_visual_1999} examine widget identification in
-IBOTS and VisMap.  Also
-see~\cite{potter_triggers_1992}~\cite{amant_image_2005}~\cite{lieberman_visual_2001}.  Visual
-identification of widgets and UIs may also have also been used in Olsen et al.'s ScreenCrayons work
-that links annotations to arbitrary screen elements~\cite{olsen_jr_implementing_1999}, and in Tan et
-al.'s work to interactively subdivide windows with a copy-paste metaphor~\cite{tan_wincuts_2004}.
-\textbf{Andrew: Check on this.}
-
-More recently, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI elements from
-screen captures, using template matching for small UI elements and voting based on invariant local
-features for large elements.  In application, Sikuli allows users to search for documentation
-related to screenshots taken of UI elements, and to script GUI tasks using visual cues of the UI.
-For searching based on screenshots, 3 types of features are extracted: text from the source
-document, visual words computed from visual words from MSER-detected salient elliptical patches, and
-3-grams over widget-embedded text extracted through OCR.  For searching on the screen for saved
-screenshot images, small patterns are found via template matching and large patterns through
-invariant feature voting.
+with purely visual information, independent of any knowledge of underlying application
+implementations. For instance, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI
+elements from screen captures, using template matching for small UI elements and voting based on
+invariant local features for large elements. Sikuli allows users to search for documentation related
+to screenshots of UI elements, and to script GUI tasks using visual cues.
 
@@
 icons as input, producing metadata file of tool changes with timecodes.  With template matching at
-multiple resolutions, detection is invariant to recording resolution and some camera effects.  Their
-system cannot be run in in real-time~\cite{pongnumkul_pause-and-play_2011}.
+multiple resolutions, detection is invariant to recording resolution and some camera
+effects~\cite{pongnumkul_pause-and-play_2011}.
 
-A number of different technologies attempt to learn templates for arbitrary UI
-elements~\cite{chang_associating_2011}~\cite{dixon_prefab_2010}~\cite{hurst_automatically_2010}~\cite{matejka_ambient_2011}.
-Learning may require access to mouse APIs~\cite{hurst_automatically_2010} and accessibility
-APIs~\cite{chang_associating_2011}.
-
+% Can cite these but we need more space for actual content: ~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
 Prefab identifies GUI elements with GUI specific visual features~\cite{dixon_prefab_2010}, which
-enables overlay of advanced interactions on existing
-interfaces~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.  \textbf{Andrew: Check up on
-this initial description.  I'm also not sure if Prefab actually belongs in this conceptual group.}
-To delve into the technical implementations of the Prefab pixel-based matching algorithm, we report
-from~\cite{dixon_general-purpose_2012}.  Prefab identifies interface elements using a library of
-prototypes.  This uses two strategies: exact matches of prototype pixels against an image, and
-modelining the prototype background and differencing pixel in an image to identify foreground
-interface elements.  Prefab generalizes from example images to models which contain parts like exact
-pixel features, or regions or areas of variable size or repeating patterns.  It organizes the entire
-interface into a hierarchy.
+enables overlay of advanced interactions on existing interfaces.  Prefab identifies interface
+elements using a library of prototypes.  This uses two strategies: exact matches of prototype pixels
+against an image, and modelining the prototype background and differencing pixel in an image to
+identify foreground interface elements.  Prefab generalizes from example images to models which
+contain parts like exact pixel features, or regions or areas of variable size or repeating patterns.
+It organizes the entire interface into a hierarchy.
 
@@
 
-\section{Video Classification}
+\section{Video Classification}\label{sec:daniel}
 
-This will be Daniel's section. I'm probably not going to include any subsections to save time.
-
-Figure~\ref{fig:alex_net} shows our accuracy results for the two AlexNet networks we trained.
-
-Figure~\ref{fig:per_class} shows our per-class accuracy results for the ``no noise'' AlexNet
-network.
+As a first step in the information extraction pipeline, we consider the following classification
+question: given a video tutorial, what application is it about? As an extra challenge, we will only
+assume we have access to the raw frames, and not other meta data such as the video title, etc.
+(Knowing that a video is called ``Eclipse Tutorial \#5'' would make the task too easy.) The
+rationale for analyzing this classification problem is that if we know the application that forms
+the basis of the video tutorial, then we can further specialize information extraction procedures.
+For instance, we might develop templates for matching Eclipse menu items, which would be deployed
+only if we are reasonably confident that a video tutorial is actually about Eclipse. Furthermore, if
+a video contains multiple applications (e.g., a video might contain Excel, Powerpoint, and other
+Microsoft Office products), we might be able to segment the video based on application type, which
+relates to the need to partition videos.
 
@@
 
-Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show visualizations of the 96 filters in
-the first layer of AlexNet, each of which has dimension $55\times 55$. These were taken for the
-model that had 1000 iterations of training.
+To collect training data, we used the open source \texttt{youtube-dl} software to download videos
+from YouTube into mp4 format. We restricted our focus to videos about Eclipse, Excel, Photoshop, and
+SketchUp, and we extracted from playlists to maintain consistency among the four classes. Most
+videos were four to fifteen minutes long.  Then, we used the open source \texttt{ffmpeg} software to
+extract one frame per second from each video, which resulted in a set of about 110240 JPG images,
+roughly evenly split among the four classes. We randomly divided this into training, validation, and
+testing sets, with 52000 training images (13000 per class), 8000 validation images (2000 per class),
+and 1000 testing images (250 per class). All images were resized to $256\times 256$ pixels.
+
+We observed that many of the videos we found had specialized beginning and ending scenes that
+created frames that were different from what we would expect for those videos. For instance, the
+SketchUp videos we found had a lengthy 10-15 second introductory scene that was the same for all
+videos, but was not very similar to the various scenes inside the actual tutorial portion of the
+videos. Thus, we created two datasets: one with all the frames we extracted, and one with the
+\emph{first and last ten frames removed} for each video. Since we had one frame per second, this was
+equivalent to ``cropping'' each video by ten seconds on both sides. This cropped dataset, which also
+included cropped validation and testing frames, was termed the ``no noise'' data.
+
+To train our network, we used CAFFE's pre-provided AlexNet architecture, but increased the momentum
+from 0.9 to 0.99 and decreased the base learning rate from 0.01 to 0.001. We had fairly small batch
+size of 32 images, so our updates are relatively noisy. We ran training for 1000 iterations on both
+datasets and saved every 20th architecture for testing purposes.
+
+Figure~\ref{fig:alex_net} shows our accuracy results for the two AlexNet networks we trained on the
+test set of 1000 images. One can see that the architecture trained on all the data performed
+inconsistently on its testing data, and its accuracy eventually leveled off at 25 percent since it
+always guessed that frames belonged to SketchUp videos. In contrast, the architecture trained and
+tested on ``noiseless'' data performed about as good as we could have hoped for, with accuracy
+peaking at 96.1 percent after 1000 iterations.
+
+We also decided to investigate per-class accuracy results to see if certain types of video frames
+were harder to learn than others. Figure~\ref{fig:per_class} shows our per-class accuracy results
+for the ``no noise'' AlexNet network. For the first few iterations, accuracy varies wildly among the
+classes since it is not uncommon for the network to always pick one class. After that, it seems
+clear that the SketchUp videos are the hardest to learn since the black curve regularly shows worse
+accuracy results than the others. Fortunately, by the time we reach about 500 iterations, our
+network can correctly classify the vast majority of images across all four classes.
+
+We then investigated the 96 filters for the first layer of the AlexNet architecture, each of which
+has dimension $55\times 55$. Figures~\ref{fig:filters_all} and~\ref{fig:filters_nonoise} show
+visualizations for the two architectures taken after 1000 iterations of training. There are some
+interesting patterns present, such as straight lines and rough, curved shapes.
 
@@
 
-\section{Locating Menus in a Frame Sequence}
+\section{Locating Menus in a Frame Sequence}\label{andrew}
 
 This will be Andrew's section.
-
-\subsection{Data}
 
@@
 
-\subsection{Implementation}
 Here's a figure of our (edit: Andrew's) pipeline.  \textbf{Andrew: Add figure of pipeline.}
-
-\subsection{Menu Location Results}
 

### 2015-05-11 paper/main.tex
Cleaned up Sections 1, 2, and 4. I left 1.5 pages for section 3 (Andrew's section). Ideally, we will put all references on page 5. They can't be this strict about page limits.

@@
 
-\section{Introduction}
+\begin{abstract}
+In this project, we present two main contributions. First, we show that a standard AlexNet neural
+network with minimal tweaking can accurately recognize frames belonging to a class of videos.
+Second, we present a pipeline for detecting menus within a video frame sequence. We then discuss how
+these two stages might be combined to enhance the process of extracting information from videos.
+\end{abstract}
 
-In this project, we present two main contributions. First, we show that a standard neural network
-following the AlexNet architecture with minimal tweaking can accurately recognize frames belonging
-to a class of videos.  Second, we present a pipeline for detecting menus within a video frame
-sequence. We then discuss how these two stages might be combined to enhance the process of
-extracting information from videos.
-
-\subsection{Motivation}
+\section{Introduction and Motivation}
 
@@
 pongnumkul_pause-and-play_2011}.  One strength of video tutorials is that users can directly observe
-expert use, which can serve as a strong learning aid. Grossman \& Fitzmaurice showed that short,
-10-25 second contextually-related videos were more effective to help users accomplish tasks than
-traditional text-based tutorials~\cite{grossman_toolclips_2010}.  Unfortunately, video tutorials
-have drawbacks. Navigation issues could lead to misunderstanding of content, and users may not be
-able to keep up with the pace of instruction. Researchers working with longer, 2-3 minute
-task-oriented tutorials found that users performed better with text tutorials than videos because
-users could not work at the same pace as the video~\cite{grabler_generating_2009}.
+expert use. Grossman \& Fitzmaurice showed that short, 10-25 second contextually-related videos were
+more effective to help users accomplish tasks than traditional text-based
+tutorials~\cite{grossman_toolclips_2010}.  Unfortunately, navigation issues could lead to
+misunderstanding of content, and users may not be able to keep up with the pace of instruction.
+Researchers working with longer, 2-3 minute task-oriented tutorials found that users performed
+better with text tutorials than videos because users could not work at the same pace as the
+video~\cite{grabler_generating_2009}. In general, research on instructional videos shows a need to
+segment videos to emphasize various steps. Our goal in this project is to explore how to segment
+existing videos by using computer vision techniques.
 
-In general, research on instructional videos point shows a need to segment videos to emphasize
-certain steps. One way to automatically segment existing videos is to develop techniques for
-detecting locations of certain menu actions in videos. Our goal, therefore, is to do this by
-utilizing computer vision techniques.
-
-\subsection{Related Work}
-
-By examining pixels, many have succeeded at reverse engineering user interfaces and interactions
-with purely visual information, independent of any knowledge of underlying application
-implementations. For instance, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI
-elements from screen captures, using template matching for small UI elements and voting based on
-invariant local features for large elements. Sikuli allows users to search for documentation related
-to screenshots of UI elements, and to script GUI tasks using visual cues.
+By examining pixels, many have succeeded at reverse engineering user interfaces (UIs) and
+interactions with purely visual information, independent of underlying application knowledge.  For
+instance, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI elements from screen
+captures by using template matching for small UI elements and voting based on invariant local
+features for large elements. Sikuli allows users to search for documentation related to screenshots
+of UI elements, and to script GUI tasks using visual cues.
 
@@
 in compressed, low-resolution video tutorials.  The system takes a tool palette template and tool
-icons as input, producing metadata file of tool changes with timecodes.  With template matching at
-multiple resolutions, detection is invariant to recording resolution and some camera
+icons as input and produces a metadata file of tool changes with timecodes.  With template matching
+at multiple resolutions, detection is invariant to recording resolution and some camera
 effects~\cite{pongnumkul_pause-and-play_2011}.
@@
 % Can cite these but we need more space for actual content: ~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
-Prefab identifies GUI elements with GUI specific visual features~\cite{dixon_prefab_2010}, which
+Prefab identifies GUI elements with GUI-specific visual features~\cite{dixon_prefab_2010}, which
 enables overlay of advanced interactions on existing interfaces.  Prefab identifies interface
-elements using a library of prototypes.  This uses two strategies: exact matches of prototype pixels
-against an image, and modelining the prototype background and differencing pixel in an image to
-identify foreground interface elements.  Prefab generalizes from example images to models which
-contain parts like exact pixel features, or regions or areas of variable size or repeating patterns.
-It organizes the entire interface into a hierarchy.
-
-Waken contributes to this space by discovering cursor shapes, clicking actions, icons, tooltips and
+elements using two strategies: exact matches of prototype pixels, and models of the background and
+pixel differences to identify foreground interface elements. Waken~\cite{banovic_waken_2012}
+contributes to this research by discovering cursor shapes, clicking actions, icons, tooltips and
 menus, all by examining the difference between frames of UI video.  They do this by making
 assumptions about how the image of icons change during hover and press actions.  Detection of the
-cursor and icons in later frames is performed by template matching~\cite{banovic_waken_2012}.  We
-rely on techniques similar to those in Waken to establish when menus have been activated and menu
-items selected.
+cursor and icons in later frames is performed by template matching.  We rely on techniques similar
+to those in Waken to establish when menus have been activated and menu items selected.
 
@@
 As a first step in the information extraction pipeline, we consider the following classification
-question: given a video tutorial, what application is it about? As an extra challenge, we will only
-assume we have access to the raw frames, and not other meta data such as the video title, etc.
-(Knowing that a video is called ``Eclipse Tutorial \#5'' would make the task too easy.) The
-rationale for analyzing this classification problem is that if we know the application that forms
-the basis of the video tutorial, then we can further specialize information extraction procedures.
-For instance, we might develop templates for matching Eclipse menu items, which would be deployed
-only if we are reasonably confident that a video tutorial is actually about Eclipse. Furthermore, if
-a video contains multiple applications (e.g., a video might contain Excel, Powerpoint, and other
-Microsoft Office products), we might be able to segment the video based on application type, which
-relates to the need to partition videos.
+question: given a video tutorial, what application is it about? We only allow access to the raw
+frames, and not metadata such as the video title.  This is an important problem because if we know
+the application type of the video tutorial, then we can deploy class-specific extraction procedures,
+such as template matching tools based on (for instance) Eclipse videos. Furthermore, if a video
+contains multiple applications (e.g., a Microsoft Office video might contain Excel, Powerpont, and
+other related products) we might be able to segment the video based on application type, which ties
+in to one of our original project goals.
 
@@
 \centering
-  \begin{minipage}{.48\textwidth}
+  \begin{minipage}{.4\textwidth}
   \centering
@@
   \end{minipage}\hfill
-  \begin{minipage}{.48\textwidth}
+  \begin{minipage}{.4\textwidth}
   \centering
@@
 
-To collect training data, we used the open source \texttt{youtube-dl} software to download videos
-from YouTube into mp4 format. We restricted our focus to videos about Eclipse, Excel, Photoshop, and
-SketchUp, and we extracted from playlists to maintain consistency among the four classes. Most
-videos were four to fifteen minutes long.  Then, we used the open source \texttt{ffmpeg} software to
-extract one frame per second from each video, which resulted in a set of about 110240 JPG images,
-roughly evenly split among the four classes. We randomly divided this into training, validation, and
+To collect training data, we used the \texttt{youtube-dl} software to download YouTube videos into
+mp4 format. We restricted our focus to videos about Eclipse, Excel, Photoshop, and SketchUp, and we
+extracted from playlists to maintain consistency. Then we used the \texttt{ffmpeg} software to
+extract one frame per second from each video, which resulted in a set of 110240 JPG images, roughly
+evenly split among the four classes.
+
+We observed that many of our videos had special introductory and concluding scenes that were of a
+different style than the true content of the video. Thus, we created two datasets: one with
+\emph{all} the frames, and one with the \emph{first and last ten frames removed} for each video.
+Since we had one frame per second, this was equivalent to ``cropping'' each video by ten seconds on
+both sides. This cropped dataset, which also included cropped validation and testing frames, was
+termed the ``no noise'' data. We randomly divided both datasets into training, validation, and
 testing sets, with 52000 training images (13000 per class), 8000 validation images (2000 per class),
-and 1000 testing images (250 per class). All images were resized to $256\times 256$ pixels.
-
-We observed that many of the videos we found had specialized beginning and ending scenes that
-created frames that were different from what we would expect for those videos. For instance, the
-SketchUp videos we found had a lengthy 10-15 second introductory scene that was the same for all
-videos, but was not very similar to the various scenes inside the actual tutorial portion of the
-videos. Thus, we created two datasets: one with all the frames we extracted, and one with the
-\emph{first and last ten frames removed} for each video. Since we had one frame per second, this was
-equivalent to ``cropping'' each video by ten seconds on both sides. This cropped dataset, which also
-included cropped validation and testing frames, was termed the ``no noise'' data.
+and 1000 testing images (250 per class).
 
 To train our network, we used CAFFE's pre-provided AlexNet architecture, but increased the momentum
-from 0.9 to 0.99 and decreased the base learning rate from 0.01 to 0.001. We had fairly small batch
-size of 32 images, so our updates are relatively noisy. We ran training for 1000 iterations on both
-datasets and saved every 20th architecture for testing purposes.
+from 0.9 to 0.99 and decreased the base learning rate from 0.01 to 0.001. We did this because our
+batch size of 32 was smaller than the standard 256, so our updates would have been noisier on
+average. We ran training for 1000 iterations on both datasets and saved every 20th architecture for
+testing purposes.
 
-Figure~\ref{fig:alex_net} shows our accuracy results for the two AlexNet networks we trained on the
-test set of 1000 images. One can see that the architecture trained on all the data performed
-inconsistently on its testing data, and its accuracy eventually leveled off at 25 percent since it
-always guessed that frames belonged to SketchUp videos. In contrast, the architecture trained and
-tested on ``noiseless'' data performed about as good as we could have hoped for, with accuracy
+Figure~\ref{fig:alex_net} shows accuracy results for the two AlexNet networks we trained on the
+1000-image test set. The architecture trained on all the data performed inconsistently and its
+accuracy eventually leveled off at 25 percent since it always guessed that frames belonged to
+SketchUp videos. In contrast, the ``noiseless'' data architecture performed very well, with accuracy
 peaking at 96.1 percent after 1000 iterations.
 
-We also decided to investigate per-class accuracy results to see if certain types of video frames
-were harder to learn than others. Figure~\ref{fig:per_class} shows our per-class accuracy results
-for the ``no noise'' AlexNet network. For the first few iterations, accuracy varies wildly among the
-classes since it is not uncommon for the network to always pick one class. After that, it seems
-clear that the SketchUp videos are the hardest to learn since the black curve regularly shows worse
-accuracy results than the others. Fortunately, by the time we reach about 500 iterations, our
-network can correctly classify the vast majority of images across all four classes.
+We also investigated per-class accuracy results to see if certain classes of video frames were
+harder to learn than others. Figure~\ref{fig:per_class} shows results for the ``no noise'' AlexNet
+network. It is clear that SketchUp videos are initially the hardest to learn to identify;
+fortunately, by the time we reach 500 iterations, our network can correctly classify the vast
+majority of images across all four classes.
 
@@
 visualizations for the two architectures taken after 1000 iterations of training. There are some
-interesting patterns present, such as straight lines and rough, curved shapes.
+interesting patterns, such as straight lines and rough, curved shapes.
 
@@
 \centering
-  \begin{minipage}{.4\textwidth}
+  \begin{minipage}{.35\textwidth}
   \centering
@@
   \end{minipage}\hfill
-  \begin{minipage}{.4\textwidth}
+  \begin{minipage}{.35\textwidth}
   \centering
@@
 
-Finally, we performed a brief, informal experiment where we applied the neural network to videos that
-were not part of our training or testing data. We chose one video for each of the four classes by
-searching on Google Video ``X tutorial'' where ``X'' was replaced by one of the four video names.
-The first video that was between 5 and 20 minutes long, and that was not already part of our
-training/testing data, was selected. We extracted one frame per second for the four videos, and
-deleted the first ten and final ten frames from consideration.
+Finally, we performed a brief, informal experiment where we applied the (``noiseless'',
+1000-iteration) neural network to videos that were not part of our training or testing data. We
+chose one video for each of the four classes by searching for tutorials online; we selected the
+first video we found that was between 5 and 20 minutes long and not already part of our original
+data. We extracted one frame per second and deleted the first and last ten frames.
 
-To classify the frames, we applied our AlexNet neural network trained on the ``noiseless'' data
-after 1000 iterations. To describe the output, we use ``splits'' where $(a,b,c,d)$ indicates that
-$a, b, c,$ and $d$ frames were classified as Eclipse, Excel, Photoshop, and SketchUp, respectively.
-The splits were as follows: the Eclipse video had $(319,0,79,0)$, the Excel video had
-$(610,0,71,7)$, the Photoshop had $(1,6,416,69)$, and the SketchUp had $(9,2,233,804)$. Clearly, for
-the Eclipse, Photoshop, and SketchUp videos, the classifer was able to assign the vast majority of
-frames to the correct class. If we were using this as part of an overall data mining pipeline, our
-classifier would assign the video according to the most-assigned class, so three videos would be
-classified correctly.
-
-The Excel output is interesting, because our network thought most of the frames belonged to Eclipse
-videos. A brief look at the video indicated that it had an introductory scene that took up ninety
-seconds (and we only deleted the first 10 frames) and that it was about a newer version of Excel
-(2013) than the ones that were trained in our network (2007). Still, it is unfortunate but shows
-that we need to be able to provide a wider variety of training data.
+To describe the output, consider a ``split'' to be $(a,b,c,d)$, which indicates that $a, b, c,$ and
+$d$ frames were classified as Eclipse, Excel, Photoshop, and SketchUp, respectively.  The Eclipse
+video had $(319,0,79,0)$, the Excel video had $(610,0,71,7)$, the Photoshop had $(1,6,416,69)$, and
+the SketchUp had $(9,2,233,804)$. Clearly, for the Eclipse, Photoshop, and SketchUp videos, the
+classifier was able to assign the vast majority of frames to the correct class. The Excel output is
+unfortunate, but intriguing because our network thought most of the frames belonged to Eclipse
+videos. That video we chose was about a newer Excel version (2013) than the one we trained on
+(2007).  With a wider variety of Excel frames, we would likely be able to classify that video
+correctly.
 
@@
 
-TODO (combining the two because we don't have a lot of space!)
-
-We freakin' rock.
+We have described a classifier that can classify video frames, and a pipeline for extracting menus
+from videos. Future would would ideally integrate both steps in an overall data mining pipeline by
+using class knowledge to develop more specific templates for menu extraction.
 

### 2015-05-11 paper/main.tex
Paper: Added my draft of a section.

@@
 
-This will be Andrew's section.
+Recent work~\cite{banovic_waken_2012} has shown how to extract templates for cursors and icons by
+monitoring pixel differences across frames.  While there has been some initial efforts
+towards recognizing tooltips and menus~\cite{banovic_waken_2012}, this task still lacks a
+satisfying solution, given that reliable techniques to identify menu-based events could enable
+automatic assessment of usability from UI video.
 
-Answer these questions:
-\begin{enumerate}[noitemsep]
-\item What is our dataset?
-\item How did we construct/acquire it?
-\item What's its size?
-\item (optional) How will we improve it in the future?
-\end{enumerate}
+Detecting menus based on pixel difference between frames poses three challenges.  First, compressed 
+video contains frame-to-frame noise that clouds the signal of a change in UI appearance, 
+particularly if UI widgets tend to fade in or out gradually.  Second, these menus occlude
+heterogeneous backgrounds (photos in Photoshop, colorful code in the IDE), making the difference
+at each individual pixel highly-varied relative to its neighbors when a new object appears in the
+foreground, even if it is of homogeneous color.  Third, depending on the operating system, 
+the edges dividing menus from ribbons and borders in the main UI may be subtle compared to the
+internal edges in a menu caused by text or internal horizontal lines that separate groups of options.
+This makes it impossible to apply traditinoal segmentation techniques to extract menu regions from 
+static images.
 
-Here's a figure of our (edit: Andrew's) pipeline.  \textbf{Andrew: Add figure of pipeline.}
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline1}
+        \caption{}
+        \label{fig:pipeline1}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline2}
+        \caption{}
+        \label{fig:pipeline2}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline3}
+        \caption{}
+        \label{fig:pipeline3}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline4}
+        \caption{}
+        \label{fig:pipeline4}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline5}
+        \caption{}
+        \label{fig:pipeline5}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \includegraphics[width=\textwidth]{fig/pipeline6}
+        \caption{}
+        \label{fig:pipeline6}
+    \end{subfigure}
+    \caption{Our pipeline for extracting UI menu locations from a sequence of video frames.}
+\end{figure}
 
-Here we (edit: Andrew) want to touch upon:
-\begin{enumerate}[noitemsep]
-\item How reliably can we classify UI events?
-\item How long does it take for us to process one minute of video?  What are
-the practical implications of this?
-\item Some images that show recognition results for a few representative
-screenshots of user interfaces.
-\end{enumerate}
+We propose a method for extracting regions containing menus based on frame-to-frame pixel
+differences.  We address the first two of the three detection challenges described above.
+
+Our pipeline comprises three major steps.  First, we perform \emph{temporal smoothing}
+of frame-to-frame pixel differences by averaging pixel differences over a window of size 10 
+(Figure~\ref{fig:pipeline2}).  This reduces noise due to compression and enables us to detect
+menus that fade in instead of appearing instantly.  10 frames is one-third of a second in a $29.97fps$ video, 
+long enough to capture the entire fade-in of a menu in Windows 7 (3-5 frames)
+and short enough to avoid capturing multiple menu actions in the same window.  Second, we \emph{coalesce
+pixel differences} into a blob that spans the menu.  We perform heavy smoothing to remove
+discontinuities in edge segments and bridge blobs from menu text (Figure~\ref{fig:pipeline3}).
+We binarize the smoothed image at a heuristically-determined threshold (Figure~\ref{fig:pipeline4}).
+Finally, we use existing methods for contour detection to trace the blob outline (Figure~\ref{fig:pipeline5}),
+from which we take a rectangular bounding box as a region proposal (Figure~\ref{fig:pipeline6}).
+We ignore all blobs that are smaller than 5000 pixels (around $70x70$ pixels square) to filter
+out false positives from noisy regions of the screen.
+
+To test our technique, we found 33 menu appearance events in 5 tutorial videos about Android development
+in the Eclipse IDE.  This sample covered 3 different operating systems.
+For each menu appearance, we selected the first frame where the menu was fully opaque in the video
+(i.e., after fade-in) and manually determined its ground truth bounding box.
+
+The quality of our region proposals is promising.  Our technique locates region proposal that
+overlapping with the ground truth in 30/33 (91\%) of the test events.  We see an average 
+intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
+for all menu appearances.  We note that the strength of our technique varies depending
+on operating system.  For example, our system produced low-overlap region proposals
+on a computer like Windows 2000, where the menu and application background color were likely
+indistinguishable to our difference detection methods (Figure~\ref{fig:proposal5}, Figure~\ref{fig:proposal6}).
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal1}
+        \caption{}
+        \label{fig:proposal1}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal2}
+        \caption{}
+        \label{fig:proposal2}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal3}
+        \caption{}
+        \label{fig:proposal3}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal4}
+        \caption{}
+        \label{fig:proposal4}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal5}
+        \caption{}
+        \label{fig:proposal5}
+        \vspace*{2mm}
+    \end{subfigure}
+    \begin{subfigure}{0.15\textwidth}
+        \includegraphics[width=\textwidth]{fig/proposal6}
+        \caption{}
+        \label{fig:proposal6}
+        \vspace*{2mm}
+    \end{subfigure}
+\end{figure}
+
+Our technique shows promise for extracting menu regions from UI videos.  We took preliminary efforts
+to determine how to detect frame indexes where menus appear.  We hypothesize that frames with a 
+high absolute pixel difference over their predecessors contained UI events.  To test his hypothesis, 
+we extracted frames from one tutorial video for which the absolute pixel difference in the last 10
+frames was in the 90th percentile of all differences.  Taking a sample of 50 of these frames, we confirmed that
+\emph{nearly all} frames in this percentile showed a UI event in progress.  Of these, only 6 (12\%) 
+were menu appearances or disappearances.  We conclude that while pixel difference-based inspection of frames may lead to
+high precision detection of UI events in general, more specialized techniques are needed to
+delineate menu-based UI events from application switches, window repainting, and window
+appearances and disappearances in the future.
 

### 2015-05-12 paper/main.tex
Minor errors

@@
 internal edges in a menu caused by text or internal horizontal lines that separate groups of options.
-This makes it impossible to apply traditinoal segmentation techniques to extract menu regions from 
+This makes it impossible to apply traditional segmentation techniques to extract menu regions from 
 static images.
@@
 
-The quality of our region proposals is promising.  Our technique locates region proposal that
-overlapping with the ground truth in 30/33 (91\%) of the test events.  We see an average 
+The quality of our region proposals is promising.  Our technique locates region proposals that
+overlap with the ground truth in 30/33 (91\%) of the test events.  We see an average 
 intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
@@
 to determine how to detect frame indexes where menus appear.  We hypothesize that frames with a 
-high absolute pixel difference over their predecessors contained UI events.  To test his hypothesis, 
+high absolute pixel difference over their predecessors contained UI events.  To test this hypothesis, 
 we extracted frames from one tutorial video for which the absolute pixel difference in the last 10

### 2015-05-12 paper/main.tex
Revised the main file.

@@
 
-The proliferation of video tutorials on using different software raises new research questions on
-how to improve users' ability to learn from them~\cite{matejka_ambient_2011,
-pongnumkul_pause-and-play_2011}.  One strength of video tutorials is that users can directly observe
-expert use. Grossman \& Fitzmaurice showed that short, 10-25 second contextually-related videos were
-more effective to help users accomplish tasks than traditional text-based
-tutorials~\cite{grossman_toolclips_2010}.  Unfortunately, navigation issues could lead to
-misunderstanding of content, and users may not be able to keep up with the pace of instruction.
-Researchers working with longer, 2-3 minute task-oriented tutorials found that users performed
-better with text tutorials than videos because users could not work at the same pace as the
-video~\cite{grabler_generating_2009}. In general, research on instructional videos shows a need to
-segment videos to emphasize various steps. Our goal in this project is to explore how to segment
-existing videos by using computer vision techniques.
+In recent years, video tutorials for learning to use software have proliferated online.  
+This has attracted interest in improving users' ability to learn from them~\cite{matejka_ambient_2011,
+pongnumkul_pause-and-play_2011}.  Video tutorials appear to be beneficial for
+some learning tasks.  Grossman \& Fitzmaurice showed that short, 10-25 second contextually-related videos were
+more effective in helping users accomplish tasks than traditional text-based
+tutorials~\cite{grossman_toolclips_2010}.
 
-By examining pixels, many have succeeded at reverse engineering user interfaces (UIs) and
+Unfortunately, navigation issues lead to misunderstandings, and users can't always keep up with the pace of instruction.
+Researchers found that when provided with 2-3 minute task-oriented tutorials, users perform
+better with text tutorials than videos because users cannot work at the same pace as the
+video~\cite{grabler_generating_2009}. This work points to a need to better segment, index, and 
+enable navigation of videos to improve users' abilities to adapt to the pace of instruction.
+In our project, we investigate techniques for \emph{understanding applications and menu events in UI tutorial videos through
+computer vision}, with the intent to enable new methods of segmenting, indexing and navigating tutorial videos.
+
+We build upon past work that visually reverse engineers user interfaces (UIs).
+By examining pixels, many have succeeded at reverse engineering UIs and
 interactions with purely visual information, independent of underlying application knowledge.  For
 instance, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to identify GUI elements from screen
-captures by using template matching for small UI elements and voting based on invariant local
-features for large elements. Sikuli allows users to search for documentation related to screenshots
-of UI elements, and to script GUI tasks using visual cues.
+captures with template matching for small UI elements and voting based on invariant local
+features for large elements. Prefab identifies GUI elements with GUI-specific visual features~\cite{dixon_prefab_2010}
+to provide an overlay of advanced interactions on existing interfaces.  The system identifies interface
+elements using two strategies: exact matches of prototype pixels, and models of the background and
+pixel differences to identify foreground interface elements.
 
-Pause-and-Play extends the template matching approach of Sikuli to detect tool-selection UI events
-in compressed, low-resolution video tutorials.  The system takes a tool palette template and tool
-icons as input and produces a metadata file of tool changes with timecodes.  With template matching
-at multiple resolutions, detection is invariant to recording resolution and some camera
-effects~\cite{pongnumkul_pause-and-play_2011}.
-
-% Can cite these but we need more space for actual content: ~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
-Prefab identifies GUI elements with GUI-specific visual features~\cite{dixon_prefab_2010}, which
-enables overlay of advanced interactions on existing interfaces.  Prefab identifies interface
-elements using two strategies: exact matches of prototype pixels, and models of the background and
-pixel differences to identify foreground interface elements. Waken~\cite{banovic_waken_2012}
-contributes to this research by discovering cursor shapes, clicking actions, icons, tooltips and
+Perhaps most related, Waken~\cite{banovic_waken_2012}
+contributes to this research direction by discovering cursor shapes, clicking actions, icons, tooltips and
 menus, all by examining the difference between frames of UI video.  They do this by making
@@
 cursor and icons in later frames is performed by template matching.  We rely on techniques similar
-to those in Waken to establish when menus have been activated and menu items selected.
+to those in Waken to detect when and where menus appear in UI videos.
 
@@
 Recent work~\cite{banovic_waken_2012} has shown how to extract templates for cursors and icons by
-monitoring pixel differences across frames.  While there has been some initial efforts
+monitoring pixel differences across frames of UI videos.  While there have been some initial efforts
 towards recognizing tooltips and menus~\cite{banovic_waken_2012}, this task still lacks a
 satisfying solution, given that reliable techniques to identify menu-based events could enable
-automatic assessment of usability from UI video.
+automatic assessment of usability from UI video and provide new ways of indexing tutorial videos
+based on complex user interface events.
 
-Detecting menus based on pixel difference between frames poses three challenges.  First, compressed 
+It is challenging to detect menus based on pixel difference between frames for three reasons.  First, compressed 
 video contains frame-to-frame noise that clouds the signal of a change in UI appearance, 
-particularly if UI widgets tend to fade in or out gradually.  Second, these menus occlude
+particularly if UI widgets tend to fade in or out gradually.  Second, when menus appear, they occlude
 heterogeneous backgrounds (photos in Photoshop, colorful code in the IDE), making the difference
@@
 We binarize the smoothed image at a heuristically-determined threshold (Figure~\ref{fig:pipeline4}).
-Finally, we use existing methods for contour detection to trace the blob outline (Figure~\ref{fig:pipeline5}),
+Finally, we use existing methods for \emph{contour detection} to trace the blob outline (Figure~\ref{fig:pipeline5}),
 from which we take a rectangular bounding box as a region proposal (Figure~\ref{fig:pipeline6}).
@@
 intersection-over-union of 74\%.  Our technique produced only 2 false positive bounding rectangles 
-for all menu appearances.  We note that the strength of our technique varies depending
-on operating system.  For example, our system produced low-overlap region proposals
-on a computer like Windows 2000, where the menu and application background color were likely
+for all menu appearances.  We note that the strength of our technique varies by
+operating system.  For example, our system produced low-overlap region proposals
+on a Windows 2000-style interface, where the menu and application background color were likely
 indistinguishable to our difference detection methods (Figure~\ref{fig:proposal5}, Figure~\ref{fig:proposal6}).
@@
 We have described a classifier that can classify video frames, and a pipeline for extracting menus
-from videos. Future would would ideally integrate both steps in an overall data mining pipeline by
+from videos. Future work would ideally integrate both steps in an overall data mining pipeline by
 using class knowledge to develop more specific templates for menu extraction.

### 2015-05-12 paper/main.tex
Minor fixes

@@
 contributes to this research direction by discovering cursor shapes, clicking actions, icons, tooltips and
-menus, all by examining the difference between frames of UI video.  They do this by making
+menus, all by examining the difference between frames of UI videos.  They do this by making
 assumptions about how the image of icons change during hover and press actions.  Detection of the
@@
   \includegraphics[width=1\linewidth]{PerClassPerformance1000}
-  \caption{AlexNet per-class accuracy results for the network trained on ``no noise'' data.}
+  \caption{AlexNet per-class accuracy results for our ``noiseless'' network.}
   \label{fig:per_class}
@@
   \includegraphics[width=1\linewidth]{Filters_All1000}
-  \caption{Visualization of filters from the network trained on all our image data.}
+  \caption{Visualization of filters from the network trained on all data.}
   \label{fig:filters_all}
@@
   \includegraphics[width=1\linewidth]{Filters_NoNoise1000}
-  \caption{Visualization of filters from the network trained on ``no noise'' image data.}
+  \caption{Visualization of filters from the network based on ``no noise'' data.}
   \label{fig:filters_nonoise}
